### 2019-08-11 ch0_frontmatter.tex
fix logos

%%%%%%%%%%%%%%%%%%%%%%%%
%%% DEFINE TITLEPAGE %%%
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{titlepage}
	\centering
	\includegraphics[width=\textwidth]{fig/DI-eps-converted-to.pdf}

	\vspace{1cm}

	\includegraphics[width=2.25cm]{fig/ITGlogo_new} 
	\vspace{2.25cm}

	{\Huge \textsf{Modelling single cell dynamics\\with trajectories and gene regulatory networks}}

@@

	{\textsf{Vakgroep Toegepaste Wiskunde, Informatica, en Statistiek\\
			Faculteit Wetenschappen, Universiteit Gent \\
			Krijgslaan 281 - S2, 9000 Gent}}
\end{titlepage}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
%%% DEFINE TITLEPAGE %%%
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{titlepage}
	\centering
	\ 
	\vfill
	{\Huge \textsf{Modelling single cell dynamics\\with trajectories and gene regulatory networks}}

@@

	\includegraphics[height=.7cm]{fig/logos/icon_UGent_WE_EN_RGB_color}\hfill
	\includegraphics[height=1cm]{fig/logos/vib_rf_inflammation_research_rgb_pos} \hfill
	\includegraphics[height=.8cm]{fig/logos/dambi_logo} \hfill
	\includegraphics[height=.7cm]{fig/logos/cmgg_myshort} \hfill
	\includegraphics[height=.7cm]{fig/logos/FWO_Logo_KleurCMYK} 
	\vspace{1cm}

	{\textsf{Vakgroep Toegepaste Wiskunde, Informatica, en Statistiek\\
			Faculteit Wetenschappen, Universiteit Gent \\
			Krijgslaan 281 - S2, 9000 Gent}}

\end{titlepage}

### 2019-08-11 ch1_introduction.tex
fix logos

\section{The cell}
The cell is the smallest unit of life, of which all known living organisms are composed. Every cell houses a plethora of biomolecular processes that allow it to adapt to changes in their environment continuously. It can be very challenging to comprehend the cellular response to a signal due to the dynamic nature of these processes. A reductionist approach to understanding a complex biological system is to study the biochemical components which it is comprised of\cite{brigandt_reductionismbiology_2017}.

@@

For example, the Human Cell Atlas (HCA) consortium\cite{regev_humancellatlas_2018} has set out to develop a comprehensive reference map of all the different types of cells in the human body. Experts in the field often metaphorically describe the HCA initiative as aiming to develop a 'Google Maps' of the human body. Even in its infancy, the HCA has profiled 3.8 million cells from 248 donors across 42 labs\cite{humancellatlasconsortium_humancellatlas_2018}, and this number is likely to increase well above one hundred million.

The sheer volume of the data generated from such highly-integrative and high-throughput experiments are not the only reason why they are so challenging to interpret. Namely, the data inherently also suffers from batch effects arising from differences between donors and labs, and also contains high levels of noise arising from the experimental profiling techniques used\cite{hon_humancellatlas_2018}. Biologists thus turn to computer scientists\footnote{or computational biologists turn to themselves} to develop new tools to tackle these problems and help biologists extract meaningful biological insights from the data.

@@

>>>>

\section{The cell}
The cell is the smallest unit of life, of which all known living organisms are composed. Every cell houses a plethora of biomolecular processes that allow it to adapt to changes in their environment continuously. It can be very challenging to comprehend the cellular response to a signal due to the dynamic nature of these processes. A reductionist approach to understanding a complex biological system is to study the biochemical components which it is comprised of \cite{brigandt_reductionismbiology_2017}.

@@

For example, the Human Cell Atlas (HCA) consortium \cite{regev_humancellatlas_2018} has set out to develop a comprehensive reference map of all the different types of cells in the human body. Experts in the field often metaphorically describe the HCA initiative as aiming to develop a 'Google Maps' of the human body. Even in its infancy, the HCA has profiled 3.8 million cells from 248 donors across 42 labs \cite{humancellatlasconsortium_humancellatlas_2018}, and this number is likely to increase well above one hundred million.

The sheer volume of the data generated from such highly-integrative and high-throughput experiments are not the only reason why they are so challenging to interpret. Namely, the data inherently also suffers from batch effects arising from differences between donors and labs, and also contains high levels of noise arising from the experimental profiling techniques used \cite{hon_humancellatlas_2018}. Biologists thus turn to computer scientists\footnote{or computational biologists turn to themselves} to develop new tools to tackle these problems and help biologists extract meaningful biological insights from the data.

@@

\section{Single cell biology}
